---
title: "MDD_TRT_analyses"
author: "Chris Camp"
date: '2022-11-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(readr)
library(ramify)
library(mgc)
library(ggplot2)
library(RColorBrewer)
library(tidyr)
library(coin)
library(reshape2)
library(corrplot)
library(Hmisc)
library(psych)
```

```{r load-data, include=FALSE, cache=TRUE}
rootdir <- 'C:/Users/chris/OneDrive - Yale University/Projects/ReliabilityAnalysis/'
all_subs_unfiltered <- read_csv(paste0(rootdir,'references/rest_df_v21_1.csv'), progress = TRUE)
all_connectomes <- read_csv(paste0(rootdir,'data/processed/connectivity_data/icc_dataframe_v21_1.csv'), progress=TRUE)
icc_summ <- read_csv(paste0(rootdir,'data/output/bootstrapped_all_icc_means_v21_1.csv'))
mdd_concat_iccs <-read_csv(paste0(rootdir, 'data/output/bootstrapped_mdd_iccs_v21_1.csv'))
hv_concat_iccs <-read_csv(paste0(rootdir, 'data/output/bootstrapped_hv_iccs_v21_1.csv'))
mdd_iccs_v2 <- read_csv(paste0(rootdir, 'data/output/mdd_iccs_v2.csv'))
mdd_iccs_v3 <- read_csv(paste0(rootdir, 'data/output/mdd_iccs_v3.csv'))

nboot <- 1000

plot_mtx <- function(Dx, main.title="Distance Matrix", xlab.title="Sample Sorted by Source", ylab.title="Sample Sorted by Source") {
  data <- melt(Dx)
  ggplot(data, aes(x=Var1, y=Var2, fill=value)) +
    geom_tile() +
    scale_fill_gradientn(name="dist(x, y)",
                         colours=c("#f2f0f7", "#cbc9e2", "#9e9ac8", "#6a51a3"),
                         limits=c(min(Dx), max(Dx))) +
    xlab(xlab.title) +
    ylab(ylab.title) +
    theme_bw() +
    ggtitle(main.title)
}
```

```{r filtering, echo=FALSE, cache=TRUE}
all_subs <- all_subs_unfiltered
all_subs$session[grepl("v1",all_subs$session)] <- "v1"
all_subs$session[grepl("v4",all_subs$session)] <- "v4"
all_subs$session[grepl("v2",all_subs$session)] <- "v2"
all_subs$session[grepl("v2",all_subs$session)] <- "v3"



all_connectomes$session[grepl("v1",all_connectomes$session)] <- "v1"
all_connectomes$session[grepl("v4",all_connectomes$session)] <- "v4"
all_connectomes$session[grepl("v2",all_connectomes$session)] <- "v2"
all_connectomes$session[grepl("v2",all_connectomes$session)] <- "v3"


# all_subs <- all_subs %>% filter(grepl("v1|v4", session)) %>% group_by(subject) %>% filter(length(session) > 1) %>% ungroup()
all_subs <- all_subs %>% filter(grepl("v1|v3", session)) %>% group_by(subject) %>% filter(length(session) > 1) %>% ungroup()
# all_subs <- all_subs %>% filter(grepl("i", session)) %>% group_by(subject) %>% filter(length(session) > 1) %>% ungroup()


change_status <- all_subs %>% group_by(subject) %>% filter(length(unique(group)) > 1)
for (i in unique(change_status$subject)){
  all_subs[all_subs$subject == i,]$group <- "MDD"
}

# all_tomes <- all_connectomes %>% filter(grepl("v1|v4", session)) %>% group_by(subject) %>% filter(length(session) == 2) %>% ungroup()
all_tomes <- all_connectomes %>% filter(grepl("v1|v3", session)) %>% group_by(subject) %>% filter(length(session) == 2) %>% ungroup()
# all_tomes <- all_connectomes %>% filter(grepl("i", session)) %>% group_by(subject) %>% filter(length(session) == 2) %>% ungroup()

mdd <- all_subs %>% filter(group == "MDD")
hv <- all_subs %>% filter(group == "HV")

mdd_tomes <- merge(mdd, all_tomes, by=c('subject','session'),all.x = TRUE)
hv_tomes <- merge(hv, all_tomes, by=c('subject','session'),all.x = TRUE)


all_subs_v1 <- filter(all_subs, grepl("v1",session))
mdd_v1 <- filter(mdd, grepl("v1",session))
hv_v1 <- filter(hv, grepl("v1",session))

nsubs <- dim(all_subs_v1)[1]
nsubs_mdd <- dim(mdd_v1)[1]
nsubs_hv <- dim(hv_v1)[1]
```

Filtering from `r length(unique(all_subs_unfiltered$subject))` subjects with `r dim(all_connectomes)[1]` scans. `r length(unique(all_subs$subject))` subjects have baseline and 1 year timepoint scans. `r dim(mdd_v1)[1]` participants are depressed (including `r length(unique(change_status$subject))` participants who received a diagnosis between scans) and `r dim(hv_v1)[1]` are healthy volunteers (HVs). F/M for all participants: `r table(all_subs_v1$sex)`. F/M for MDD participants: `r table(mdd_v1$sex)`.

```{r ICC, cache=TRUE}

mdd_concat_iccs$group <- "MDD"
hv_concat_iccs$group <- "HV"

iccs_v2_mean <- mean(mdd_iccs_v2$ICC)
iccs_v3_mean <- mean(mdd_iccs_v3$ICC)

  
all_iccs <- rbind(mdd_concat_iccs, hv_concat_iccs)

all_iccs_means <- all_iccs %>% group_by(measure, group) %>% summarise(ICC = mean(ICC))

all_iccs_means_wide <- pivot_wider(all_iccs_means, names_from = group, values_from = ICC)
all_iccs_means$group <- as.factor(all_iccs_means$group)

all_iccs_by_measure <- pivot_wider(all_iccs, names_from = measure)

icc_summ_means <- all_iccs_means %>% group_by(group) %>% summarise(mean_ICC = mean(ICC))

icc_summ_all_means <- icc_summ %>% group_by(measure) %>% summarise(mean_ICC = mean(icc_mean)) %>% pivot_wider(names_from = measure,values_from = mean_ICC)
all_mean <- mean(icc_summ$icc_mean)

wilcox.test(hv_concat_iccs$ICC, mdd_concat_iccs$ICC, alternative = "two.sided")

mdd_concat_iccs$contrasts <- mdd_concat_iccs$ICC - hv_concat_iccs$ICC
icc_contrasts <- mdd_concat_iccs[order(mdd_concat_iccs$contrasts),]
```

``` {r fingerprinting, cache=TRUE}
ses1_all <- as.matrix(all_tomes %>% filter(grepl("v1", session)) %>% ungroup() %>% select(-c(1:2)))
ses2_all <- as.matrix(all_tomes %>% filter(grepl("v2", session)) %>% ungroup() %>% select(-c(1:2)))
ses1_mdd <- as.matrix(mdd_tomes %>% filter(grepl("v1", session)) %>% ungroup() %>% select(c("1_0":"121_120")))
ses2_mdd <- as.matrix(mdd_tomes %>% filter(grepl("v2", session)) %>% ungroup() %>% select(c("1_0":"121_120")))
ses1_hv <- as.matrix(hv_tomes %>% filter(grepl("v1", session)) %>% ungroup() %>% select(c("1_0":"121_120")))
ses2_hv <- as.matrix(hv_tomes %>% filter(grepl("v2", session)) %>% ungroup() %>% select(c("1_0":"121_120")))


# write.table(ses1_all, paste0(rootdir,'ID_scripts/edge_code/data_v21_1/ses1_all.csv'), col.names=FALSE, row.names=FALSE,sep=',')
# write.table(ses2_all, paste0(rootdir,'ID_scripts/edge_code/data_v21_1/ses2_all.csv'), col.names=FALSE, row.names=FALSE,sep=',')
# write.table(ses1_mdd, paste0(rootdir,'ID_scripts/edge_code/data_v21_1/ses1_mdd.csv'), col.names=FALSE, row.names=FALSE,sep=',')
# write.table(ses2_mdd, paste0(rootdir,'ID_scripts/edge_code/data_v21_1/ses2_mdd.csv'), col.names=FALSE, row.names=FALSE,sep=',')
# write.table(ses1_hv, paste0(rootdir,'ID_scripts/edge_code/data_v21_1/ses1_hv.csv'), col.names=FALSE, row.names=FALSE,sep=',')
# write.table(ses2_hv, paste0(rootdir,'ID_scripts/edge_code/data_v21_1/ses2_hv.csv'), col.names=FALSE, row.names=FALSE,sep=',')



get_FI <- function(ses1, ses2, continuous = FALSE, null = FALSE){
  cor_mat1 <- matrix(0,nrow=dim(ses2)[1],ncol=dim(ses1)[1])
  cor_mat2 <- matrix(0,nrow=dim(ses1)[1],ncol=dim(ses2)[1])
  for (i in 1:dim(ses2)[1]){
    cor_mat1[i,] <- apply(ses1, 1, function(x) {cor.test(x,ses2[i,],method = "s", exact=FALSE)$estimate})
  }
  for (i in 1:dim(ses1)[1]){
    cor_mat2[i,] <- apply(ses2, 1, function(x) {cor.test(x,ses1[i,],method = "s", exact=FALSE)$estimate})
  }
  if (continuous == TRUE) {
    within_corrs1 = diag(cor_mat1)
    btwn_corrs1 = cor_mat1
    diag(btwn_corrs1) = 0
    btwn_corrs_avg1 = rowSums(btwn_corrs1) / (dim(btwn_corrs1)[2] - 1)
    
    within_corrs2 = diag(cor_mat2)
    btwn_corrs2 = cor_mat2
    diag(btwn_corrs2) = 0
    btwn_corrs_avg2 = rowSums(btwn_corrs2) / (dim(btwn_corrs2)[2] - 1)
    return(c(btwn_corrs_avg1,btwn_corrs_avg2))
  }
  else {
    ind1 <- cbind(1:dim(cor_mat1)[1], argmax(cor_mat1))
    ind2 <- cbind(1:dim(cor_mat2)[1], argmax(cor_mat2))
    if (null) {
      ind1[,1] <- sample(ind1[,1], length(ind1[,1]))
      ind2[,1] <- sample(ind2[,1], length(ind2[,1]))
      ind1[,2] <- sample(ind1[,2], length(ind1[,2]))
      ind2[,2] <- sample(ind2[,2], length(ind2[,2]))
    }
    FI1 <- length(ind1[ind1[,1] == ind1[,2],1])/dim(ind1)[1]
    FI2 <- length(ind2[ind2[,1] == ind2[,2],1])/dim(ind2)[1]
    return(c(FI1,FI2))
  }
}

FI_all <- get_FI(ses1_all,ses2_all)
FI_mdd <- get_FI(ses1_mdd,ses2_mdd)
FI_hv <- get_FI(ses1_hv,ses2_hv)

FI_all_null <- get_FI(ses1_all,ses2_all, null=TRUE)
FI_mdd_null <- get_FI(ses1_mdd,ses2_mdd, null=TRUE)
FI_hv_null <- get_FI(ses1_hv,ses2_hv, null=TRUE)

poisson.test(35, alternative = "two.sided")

FI_df <- data.frame(rbind(round(nsubs_mdd*mean(FI_mdd)),rbind(round(nsubs_hv*mean(FI_hv)))))
colnames(FI_df) <- "matched"
FI_df$unmatched <- rbind(nsubs_mdd - FI_df$matched[1], nsubs_hv - FI_df$matched[2])
rownames(FI_df) <- c("mdd","hv")

chi <- chisq.test(FI_df,correct=FALSE)
```


```{r discr, cache=TRUE}

corr_dat <- select(all_tomes, c("1_0":"121_120"))
subs <- all_tomes$subject
discr <- discr.test.one_sample(corr_dat, subs)


corr_dat <- select(mdd_tomes, c("1_0":"121_120"))
subs <- mdd_tomes$subject
discr_mdd <- discr.test.one_sample(corr_dat, subs)


corr_dat <- select(hv_tomes, c("1_0":"121_120"))
subs <- hv_tomes$subject
discr_hv <- discr.test.one_sample(corr_dat, subs)
```

```{r figures}
all_stats <- data.frame(cbind(rbind(mean(icc_summ_means$mean_ICC),icc_summ_means$mean_ICC[2],icc_summ_means$mean_ICC[1]),
                              rbind(mean(FI_all),mean(FI_mdd),mean(FI_hv)), 
                              rbind(mean(FI_all_null),mean(FI_mdd_null),mean(FI_hv_null)),
                              rbind(discr$stat,discr_mdd$stat,discr_hv$stat),
                              rbind(mean(discr$null),mean(discr_mdd$null),mean(discr_hv$null))),
                        row.names = c('All','MDD','HV'))
colnames(all_stats) <- c('ICC','FI','FI_null','Discr', 'Discr_null')
all_stats$sig_pos <- all_stats$Discr + .1
all_stats$sig_pos_fi <- all_stats$FI + .1


ggplot(all_stats,aes(x=rownames(all_stats),y=ICC,fill=rownames(all_stats)))+geom_bar(stat="identity", width=0.5) + ylim(0, 1) + xlab("Condition") +
  ylab("Mean ICC") + scale_color_manual(values = c("#C96468", "#FECDAA","#2A2782"),aesthetics = "fill") + 
  theme_light() + theme(legend.position="none", text = element_text(size=20))

ggplot(all_stats,aes(x=rownames(all_stats),y=FI,fill=rownames(all_stats)))+geom_bar(stat="identity", width=0.5) + ylim(0, 1) + xlab("Condition") +
  ylab("Fingerprinting Index") + scale_color_manual(values = c("#C96468", "#FECDAA","#2A2782"),aesthetics = "fill") +
  geom_segment(aes(x=(c(.75,1.75,2.75)),y=FI_null,xend=c(1.25,2.25,3.25),yend = FI_null), size = 1) +
  geom_text(aes(x=rownames(all_stats),y=sig_pos_fi),size=8,label='***') + 
  theme_light() + theme(legend.position="none", text = element_text(size=20))

ggplot(all_stats,aes(x=rownames(all_stats),y=Discr,fill=rownames(all_stats)))+geom_bar(stat="identity", width=0.5) + ylim(0, 1) + xlab("Condition") +
  ylab("Discriminability") + scale_color_manual(values = c("#C96468", "#FECDAA","#2A2782"),aesthetics = "fill") +
  geom_segment(aes(x=(c(.75,1.75,2.75)),y=Discr_null,xend=c(1.25,2.25,3.25),yend = Discr_null), size = 1) +
  geom_text(aes(x=rownames(all_stats),y=sig_pos),size=8,label='**') + 
  theme_light() + theme(legend.position="none", text = element_text(size=20)) + coord_flip()

```

```
